WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2018-12-14 paper/ms.tex
grammar-hammer

Long-term monitoring of hot Jupiter transit and occultation times
should eventually reveal two distinct processes.  First, whenever the
summed spin and orbital angular momenta in a hot Jupiter system fall
below a critical value, the system becomes unstable to tidal decay
\citep{counselman_outcomes_1973,hut_stability_1980}.  Most hot
Jupiters satisfy this condition; their orbits should be shrinking
\citep{levrard_falling_2009,matsumura_tidal_2010}.  The rate of decay
is uncertain, and depends on how friction dissipates energy carried by
gravitational tides (\citealt{ogilvie_tidal_2014} gives a review).  If
we could directly measure orbital decay rates, it would inform our
understanding of tidal dissipation.  This is important because the
dissipation rates determine the fate of the system.  During its
inspiral, if the planet fills its Roche lobe below the stellar
surface, the drag force from the stellar envelope accelerates the
inspiral, leading to a `direct-impact' merger
\citep{metzger_optical_2012,macleod_planetary_2018} Alternatively, if
the planet fills its Roche lobe above above the stellar surface, then
it could either be disrupted into an accretion disk or it could slowly
transfer mass to the star
\citep{metzger_optical_2012,valsecchi_tidally-driven_2015,jackson_tidal_2016}.
Further afield, the outcome of the eventual interaction between the
Earth and red giant Sun also hinges on the efficiency of tidal
dissipation \citep{rasio_tidal_1996}.

The second process that long-term timing studies should reveal is
apsidal precession, {\it i.e.}, rotation of the orbital ellipse within
the orbital plane. Apsidal precession has been observed extensively in
eclipsing binaries \citep[{\it e.g.},][]{
  schwarzschild_structure_1958,torres_accurate_2010,borkovits_eclipse_2015}
and has been detected in a handful of exoplanet systems, including
circumbinary planets (Kepler-413 \citealt{kostov_kepler-413b_2014};
Kepler-453 \citealt{welsh_kepler_2015}, planets orbiting rapidly
rotating stars (Kepler-13
\citealt{szabo_spin-orbit_2012,szabo_mapping_2014},~\citealt{masuda_spin-orbit_2015};
PTFO 8-8695 \citealt{barnes_measurement_2013}), and systems with
multiple interacting giant planets (Kepler-108
\citealt{mills_kepler-108_2017}; Kepler-693
\citealt{masuda_eccentric_2017}).  Apsidal precession is not regularly
observed in hot Jupiter systems, perhaps in part because their orbits
are nearly circular.  However, there are many mechanisms that could
pump hot Jupiter orbits away from circularity (see
\S~\ref{sec:apsidal_precession}, and
\citealt{bailey_understanding_2019}), which would then lead to
observable timing variations.  For hot Jupiters, the apsidal
precession is usually dominated by the quadrupolar distortion of the
planet by the star's tidal force \citep{ragozzine_probing_2009}.  The
observed precession rate in a hot Jupiter system could thus be used to
compute the planet's Love number, giving a third parameter along with
the mass and radius with which to describe the planet's interior
structure \citep[{\it e.g.},][who performed a similar procedure for
HAT-P-13b]{batygin_determination_2009}.  Measuring small
eccentricities and understanding their origin might also help us
understand the dynamical histories and inflated radii of hot Jupiters.
\citep[{\it
e.g.},][respectively]{dawson_origins_2018,ibgui_tidal_2010}

@@

>>>>

Long-term monitoring of hot Jupiter transit and occultation times
should eventually reveal two distinct processes.  First, whenever the
summed spin and orbital angular momenta in a hot Jupiter system fall
below a critical value, the system becomes unstable to tidal decay
\citep{counselman_outcomes_1973,hut_stability_1980}.  Most hot
Jupiters satisfy this condition, so their orbits should be shrinking
\citep{levrard_falling_2009,matsumura_tidal_2010}.  However the rate of decay
is uncertain, as it depends on how friction dissipates energy carried by
gravitational tides (\citealt{ogilvie_tidal_2014} gives a review).  If
we could directly measure orbital decay rates, it would inform our
understanding of tidal dissipation.  This would be important because the
dissipation rates determine the fate of the system.  During its
inspiral, if the planet fills its Roche lobe below the stellar
surface, the drag force from the stellar envelope accelerates the
inspiral, causing a `direct-impact' merger
\citep{metzger_optical_2012,macleod_planetary_2018} Alternatively, if
the planet fills its Roche lobe above the stellar surface, then
it could either be disrupted into an accretion disk or it could slowly
transfer mass to the star
\citep{metzger_optical_2012,valsecchi_tidally-driven_2015,jackson_tidal_2016}.
Further afield, the outcome of the eventual interaction between the
Earth and red giant Sun also hinges on the efficiency of tidal
dissipation \citep{rasio_tidal_1996}.

The second process that long-term timing studies should reveal is
apsidal precession, {\it i.e.}, rotation of the orbital ellipse within
the orbital plane. Apsidal precession has been observed extensively in
eclipsing binaries \citep[{\it e.g.},][]{
  schwarzschild_structure_1958,torres_accurate_2010,borkovits_eclipse_2015}.
In exoplanetary systems, precessing orbits have been detected in a
handful of cases, including circumbinary systems (Kepler-413
\citealt{kostov_kepler-413b_2014}; Kepler-453
\citealt{welsh_kepler_2015}, planets orbiting rapidly rotating stars
(Kepler-13
\citealt{szabo_spin-orbit_2012,szabo_mapping_2014},~\citealt{masuda_spin-orbit_2015};
PTFO 8-8695 \citealt{barnes_measurement_2013}), and systems with
multiple interacting giant planets (Kepler-108
\citealt{mills_kepler-108_2017}; Kepler-693
\citealt{masuda_eccentric_2017}).  Apsidal precession is not regularly
observed in hot Jupiter systems, perhaps in part because their orbits
are nearly circular.  However, there are many mechanisms that could
pump hot Jupiter orbits away from circularity (see
\S~\ref{sec:apsidal_precession}, and
\citealt{bailey_understanding_2019}), which would then lead to
observable timing variations.  For hot Jupiters, the apsidal
precession is usually dominated by the quadrupolar distortion of the
planet by the star's tidal force \citep{ragozzine_probing_2009}.  
If apsidal precession were observed in a hot Jupiter system, the
precession rate could thus be used to compute the planet's Love
number, giving a third parameter along with the mass and radius with
which to describe the planet's interior structure \citep[{\it
e.g.},][who performed a similar procedure for
HAT-P-13b]{batygin_determination_2009}.  Measuring small
eccentricities and understanding their origin might also help us
understand the dynamical histories and inflated radii of hot Jupiters.
\citep[{\it
e.g.},][respectively]{dawson_origins_2018,ibgui_tidal_2010}

@@

\clearpage
